**fabryka**

### 2025-07-15 README.Rmd
correction of fabryka article and shiny application after first round of review in PCI archaeology

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.15236695.svg)](https://doi.org/10.5281/zenodo.15236695)

@@

fabryka is an open access R *shiny* user-friendly web application dedicated to the fabric analysis of archaeological or geological assemblage. fabryka uses classical analytical procedures (Benn, rose, Schmidt and Woodcock diagrams and statistical tests on orientations) for analysing the fabrics of objects, an spatial method and new ways of spatial and statistical exploration. A descriptive article is available at <https://zenodo.org/records/15236695>.

@@

A tutorial is included in the application (*i.e.* 'Tutorial" panel) and can also be found in a dedicated article: <https://zenodo.org/records/15236695>.
'fabryka' includes an example file you can download from the application ('Upload data' subpanel).

@@

THOMAS, M. (2025). Fabryka: A web application for easily analysing & exploring the fabric of archaeological assemblages. In PCI archaeology (Version 1). Zenodo. https://doi.org/10.5281/zenodo.15236695

>>>>

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.15880861.svg)](https://doi.org/10.5281/zenodo.15880861)

@@

fabryka is an open access R *shiny* user-friendly web application dedicated to the fabric analysis of archaeological or geological assemblage. fabryka uses classical analytical procedures (Benn, rose, Schmidt and Woodcock diagrams and statistical tests on orientations) for analysing the fabrics of objects, an spatial method and new ways of spatial and statistical exploration. A descriptive article is available at <https://zenodo.org/records/15880861>.

@@

A tutorial is included in the application (*i.e.* 'Tutorial" panel) and can also be found in a dedicated article: <https://zenodo.org/records/15880861>.
'fabryka' includes an example file you can download from the application ('Upload data' subpanel).

@@

THOMAS, M. (2025). Fabryka: A web application for easily analysing & exploring the fabric of archaeological assemblages. In PCI archaeology (Version 1). Zenodo. https://doi.org/10.5281/zenodo.15880861

### 2025-07-15 fabryka_pci/article.Rmd
correction of fabryka article and shiny application after first round of review in PCI archaeology

-   use fabryka online: <https://marchaeologist.shinyapps.io/fabryka/> \smallbreak
-   source code: <https://github.com/marchaeologist/fabryka/tree/main> \smallbreak
-   Report bugs or any request: <https://github.com/marchaeologist/fabryka/issues> \smallbreak
-   github reprository doi of fabryka: <https://doi.org/10.5281/zenodo.15207419> \smallbreak
-   Zenodo repository of this article: <https://doi.org/10.5281/zenodo.15879462> \bigbreak

>>>>

-   use fabryka online: <https://marchaeologist.shinyapps.io/fabryka/> \smallbreak
-   source code: <https://github.com/marchaeologist/fabryka/tree/main> \smallbreak
-   Report bugs or any request: <https://github.com/marchaeologist/fabryka/issues> \smallbreak
-   github reprository doi of fabryka: <https://doi.org/10.5281/zenodo.15881625> \smallbreak
-   Zenodo repository of this article: <https://doi.org/10.5281/zenodo.15879462> \bigbreak
